# My First knitr Document

This is my first R Markdown file

## Global Options
Every code and result will be hide

```{r setoptions, echo=TRUE}
# library(knitr)
# opts_chunk$set(echo = FALSE, results = "hide")
# opts_chunk$set(cache = TRUE) # After the first run, results are loaded from cache
```

## Introduction
```{r computetime, echo=FALSE}
time <- format(Sys.time(), "%a %b %d %X %Y")
rand <- rnorm(1)
```

The current time is `r time`. My favorite random number is `r rand`.

Here, we're going load some data.

```{r firstchunk}
library(datasets)
data(airquality)
summary(airquality)
```

Let's first make a pairs plot of the data.

```{r}
pairs(airquality)
```

Here's a regression model of ozone on wind, solar radiation, and temperature.

```{r}
library(stats)
fit <- lm(Ozone ~ Wind + Temp + Solar.R, data=airquality)
summary(fit)
```

Here is a table of regression coefficients
```{r show table, results = "asis"}
library(xtable)
xt <- xtable(summary(fit))
print(xt, type = "html")
```

Don't echo the code
```{r simulation, echo = FALSE}
set.seed(1)
x <- rnorm(100)
mean(x)
```

Here's an unordered list:

* Fist element

* Second elements

## Simulation

Let's first simulate some data.
```{r simulation data, echo = TRUE}
x <- rnorm(100); y <- x + rnorm(100, sd = 0.5)
```

Here is a scatterplot of the data.
```{r scatterplot, fig.height=4}
par(mar = c(5,4,1,1), las = 1)
plot(x, y, main = "My Simulated Data")
```

# More Complicated Way

library(knitr)  
setwd(<working directory>)  
knit2html("document.Rmd")  
browseURL("document.html")  